The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-17 writing/draft3/draft13.tex
writing

To find the most suitable set of predictors, we adapted a step-down model building approach using the Satterthwaite's method to determine the p-values of the individual t-tests \cite{lmerTest}. To be more specific, we started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the following steps, the insignificant variables were removed one by one until only significant predictors remained. For both fixed and random effects we considered the level of significance $\alpha=0.05$.

@@

	\section{Results}\label{Results}

>>>>

@@

To find the most suitable set of fixed effects, we adapted a stepwise selection procedure to choose a model with the smallest value of the Akaike’s Information Criterion (AIC). We started  with a model which included the complete set of our weather measures in the fixed effects and random intercepts and we performed a search through the subsets off the fixed effects minimizing the AIC and allowing for steps in both `backward' and `forward' directions (removing and adding predictors). We decided to not to include the number of heatwave days and average maximum daily temperature although they slightly improve the AIC if present. The reason for not including them is that they are strongly correlated with average seasonal temperature (the value of correlation coefficient is $0.981$ for the maximum daily temperature and $0.517$ for the number of heatwave days and the p-values of both of them are smaller than $1\times10^{-6}$) and they are not significant at the level of significance $\alpha=0.05$ (their p-values were $0.121$ for the maximum daily temperature and $0.075$ for the number of heatwave days). Furthermore, including them only improved AIC by $4$ (when estimated by maximum likelihood as required for a meaningful comparison) and the signs of these variables were positive in contrary to our assumption. Hence, we concluded that the decrease in AIC and positive signs are likely to be result of their correlation with average temperature or other omitted variable and we did not include them in our model.

We further applied a series of likelihood ratio tests to test for significance of random slopes, however no subset of random slopes improved the fit, hence, our final model only included intercepts in random effects.

 allowed for both are moving and adding 
model building approach using  To be more specific, we started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the following steps, the insignificant random effects and subsequently insignificant fixed effects were removed one by one until only significant predictors remained. For random effects we considered the level of significance $\alpha=0.1$ and for fixed effects we opted for $\alpha=0.05$~\cite{lmerTest}.

\textcolor{blue}{the Satterthwaite's method to determine the p-values of the individual t-tests} \cite{lmerTest}
	\section{Results}\label{Results}
